A Machine Profile Summary

### 2022-06-14 MachineSummary/MachineSummary.Rmd
Clean up sections except boxplots

There may be multiple terms used to describe some of the information we want, as
well as different interpretations of some of the units of measure. For example
"Gigabytes" may be $1000^3$ or $1024^3$ bytes. To settle the ambiguity, the
international standard *IEC 80000-13:2008 Quantities and units - Part 13: Information science and technology*(??ref https://en.wikipedia.org/wiki/Gigabyte, https://en.wikipedia.org/wiki/ISO/IEC_80000#Part_13:_Information_science_and_technology) defines 1 Gigabyte (1 GB) as 1000^3 bytes, whereas 1 Gibibyte (1 GiB) as 1024^3 bytes.

<!-- ?? AB? Is that correct? -->

@@

For tracking work, it is important to have 
information on when the calculations were performed. 
Most computations should have a time/date stamp that is unlikely to be confused with any
other, at least in combination with a machine name and/or other tags. Here is one
suggestion based on the R `Sys.time()` function. Moreover, as we were working on opposite
sides of the globe, it could be important to either specify time zone or to work with a
single "clock" such as UTC (ref?? or expansion?)

@@

- cpu (i.e., processor)
- number of cores
- operating cycle speed (this is sometimes specific to the cpu specified )
- RAM size total
- RAM size available, possibly indicating swap space and usage
- RAM speed (which could be variable)
- GPU (i.e, additional processors) information.

@@

Clearly it is important to identify which software packages are active, and the
R `sessionInfo()` command is useful for this. However, there may be additional 
features that should be mentioned if the user has modified the software in any
way, or is using customized packages.

@@

For most uses in recording tests of R functions and packages for optimization and nonlinear 
least squares, which has been our focus, it seems that the `benchmarkme` function 
`get_sys_details()` provides more than sufficient information for our needs. 
The following script offers a possible compact solution. Users may
wish to modify this to their own particular needs.

@@

>>>>

There may be multiple terms used to describe some of the information we want, as
well as different interpretations of some of the units of measure. For example,
storage for disks or memory has decimal and binary schemes of units. Thus 
(see https://en.wikipedia.org/wiki/Gigabyte) there is a movement to use, for example, Gigabyte or GB to mean usits of 1000^3 bytes, while the Gigibyte or Gib is 1024^3.

@@

For tracking work, it is important to have 
information on when the calculations were performed. 
Most computations should have a time/date stamp that is unlikely to be confused with any
other, at least in combination with a machine name and/or other tags. Here is one
suggestion based on the R `Sys.time()` function. Moreover, as we were working on opposite
sides of the globe, it could be important to either specify time zone or to work with a
single "clock" such as UTC. R provides tools to allow this, as in the following example.

@@

- cpu (i.e., processor)
- number of cores
- operating cycle speed (this is sometimes specific to the cpu specified )

?? how do we reconcile?

<!-- From get_sys_details() -->
<!-- $cpu$model_name -->
<!-- [1] "Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz" -->

<!-- From inxi -C -->
<!-- john@M21:~$ inxi -C -->
<!-- CPU:       Topology: 6-Core model: Intel Core i5-10400 bits: 64 type: MT MCP L2 cache: 12.0 MiB  -->
<!--            Speed: 800 MHz min/max: 800/4300 MHz Core speeds (MHz): 1: 800 2: 800 3: 800 4: 800 5: 800 6: 800 7: 800 8: 800  -->
<!--            9: 800 10: 800 11: 800 12: 800  -->

?? also noted that get_sys_details shows 16 cores on my laptop, but inxi shows 8??

- RAM size total
- RAM size available, possibly indicating swap space and usage
- RAM speed (which could be variable) 
  ?? this is, as I understand the output, in inxi (for Linux). Not as far as I know in benchmarkme.

- GPU (i.e, additional processors) information. 
  ?? is there a way to get this? I don't have a GPU on my desktop machine.

@@

Clearly it is important to identify which software packages are active, and the
R `sessionInfo()` command provides this. However, there may be additional 
features that should be mentioned if the user has modified the software in any
way, or is using customized packages.

@@

For most uses in recording tests of R functions and packages for optimization and nonlinear 
least squares, which has been our focus, it seems that the `benchmarkme` function 
`get_sys_details()` provides more than sufficient information for most of our needs. 
A workable profile for our project is captured in the following script,
which allows a 1-line compact sketch of the system in use.

@@

For other applications, it is clear that users will make other choices to meet their particular needs.

Our efforts noted in this article underline the following principles.

- Relatively comprehensive tools such as package `benchmarkme` are needed to 
  make possible machine profiles to allow sensible comparison of computational 
  performance across different platforms.

- If a project uses a common software environment such as R, then the tools for
  capturing profile data should be available from that environment, and run 
  under different operating systems and hardware. In that respect, `benchmarkme`
  has been very helpful to us.

- No tool covers all the possibilities, and users may have to do extra work to 
  capture information they need. Moreover, the challenges of cross-platform 
  computing ensure that some of the results of different tools will be inaccurate.

- Summarizing capability information for computing environments to provide a 
  short-form profile is a challenge that requires care and attention. Indeed,
  it is much easier to gather a large body of information than to devise a 
  compact but useful precis of it.

We welcome conversation on how machine capability may be summarized and reported
to allow sensible comparison of computational performance of algorithms and 
systems.
